### 2018-10-10 doc/plos/text/manuscript.tex
discuss pros and cons of sensor fusion

TODO: merits and drawbacks of sensor fusion

>>>>

Herein we used a data assimilation technique which we refer to as ``sensor
fusion''. As a consequence of being derived from the Kalman filter, sensor
fusion has a number of advantages, including minimizing the expectation of
squared error, robustness to partial and missing observations, and a natural
framework for assimilating data across overlapping geographic locations.
However, sensor fusion ultimately defines a nowcast as a simple linear
combination of the available sensors. When assumptions of linearity and
normality are violated, and when covariance estimates are inaccurate, the
accuracy of resulting nowcasts suffers.
